# Kidney deceased donor post tx graft survival #
```{r}
## Set work area/libname ##
# setwd("F:\\Shared\\Organ Utilisation\\Winton Centre\\Kidney CR\\R work")
```
## Pull in libraries we need 
```{r}
library(tidyverse)
library(jsonlite)
```

## Import data ##
There are some errors in surv.csv caused by the use of different quoting characters in
hospital names. We simply avoid those hospitals in the test.
```{r}
survdata <- read.csv("surv.csv",fileEncoding = 'UTF-8-BOM')
param <- read.csv("params.csv",fileEncoding = 'UTF-8-BOM')
attach(survdata)
attach(param)

## Check data ##
head(survdata)
head(param)
```

## Define adjusted cox function 
```{r}
source("adjcox.R")
```
## Generate R Test Values
### Read in and simplify test-configuration.json 
```{r}
test.config <- function(simplifyVector = TRUE) {
  return(read_json("test-configuration.json"))
}
config <- test.config()
times <- as.integer(config$times)
days <- round(365.25 * times)
days
factors <- map_dfr(config$factors, as.data.frame)
factors

```

Poke the changed formal parameters into adjcox yielding new adjcox.perturbed function.
Then tabulate the call results.

```{r}
fn.survival <- function(fn, param.name = NULL, param.value = NULL) {
  args <- formals(fn)
  # change one value
  if(!(is.null(param.name) || is.null(param.value))) {
    args[[param.name]] <- param.value
  }
  as.function(c(args, body(fn)), parent.frame())
}
adjcox.perturbed <- function(param.name, param.value) {
  fn.survival(adjcox, param.name, param.value)()$adjsurv
}
results.at.times <- function(param.name, param.value, times) {
  f <- function(t) {fn.survival(adjcox, param.name, param.value)()$adjsurv[t]}
  map_dbl(times, f)
}
```

Accumulate results for all factors 
```{r}
days <- lapply(config$times, function(x) {round(365.25*x)})
names(days) <- c("year1", "year3", "year5")
days <- as.data.frame(days)

results.for.factor <- function (f) {
  results.at.times(f$r, f$test, days) %>% prepend(f$r)
}
```
Log the unchanged results first. adjcox with default parameters gives us the zero values. 
```{r}
acc <- results.at.times(NULL,NULL,days) %>% prepend("unchanged")
```
Then log one changed factor at a time
```{r}
for(i in seq_len(nrow(factors))) {
  acc <- rbind(acc, results.for.factor(factors[i,]))
}
acc <- rename(as.data.frame(acc), factor = V1)
```
Label with organ and tool and export to csv
```{r}
generate.results <- function(csv.path, organ, tool, acc) {
  write.csv(data.frame(organ, tool, acc), csv.path, row.names=FALSE)
}
generate.results("results.csv", "kidney", "graft", acc)
```

